### 2017-05-24 doc/categories.tex
section 5

\begin{figure}
\centering
  \includegraphics[scale=0.35]{position-new.png}
\caption{Proportion of variance in omission scores explained by the
  linear regression models
 for {\sc Sum}, {\sc Visual} and {\sc Textual} pathways, relative to
 regressing on word identity and position only. }
\label{fig:rsquared}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.35]{omission-stat/top_words.pdf}
  \caption{Distribution of omission scores per deprel label for the selected word types.}
  \label{fig:top_words}
\end{figure}
%\todo{At some point redo this with words ranked by ratio between the errors not the difference}

In order to find out some of the specific syntactic configurations leading to
increase in $R^2$ between {\sc LR word} and {\sc LR dep} predictors
in case of {\sc Visual}, we next considered all word types with
occurrence counts of at least 100 and ranked them according to how much
better, on average, {\sc LR dep} predicted their omission scores 
compared to {\sc LM +pos}.

@@

\begin{figure}
\centering
 \includegraphics[scale=0.4]{omission-stat/position-coef.png}
 \caption{Coefficients on the y-axis of {\sc LM full} corresponding to the
position variables on the x-axis.}
 \label{fig:posrqs}
\end{figure}

>>>>

\begin{figure}
\centering
  \includegraphics[scale=0.35]{position-new.pdf}
\caption{Proportion of variance in omission scores explained by the
  linear regression models
 for {\sc Sum}, {\sc Visual} and {\sc Textual} pathways, relative to
 regressing on word identity and position only. }
\label{fig:rsquared}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.35]{top_words.pdf}
  \caption{Distribution of omission scores per deprel label for the selected word types.}
  \label{fig:top_words}
\end{figure}
%\todo{At some point redo this with words ranked by ratio between the errors not the difference}

In order to find out some of the specific syntactic configurations leading to
increase in $R^2$ between {\sc LR word} and {\sc LR dep} predictors
in case of {\sc Visual}, we next considered all word types with
occurrence counts of at least 100 and ranked them according to how much
better, on average, {\sc LR +dep} predicted their omission scores 
compared to {\sc LM word}.

@@

\begin{figure}
\centering
 \includegraphics[scale=0.4]{position-coef.pdf}
 \caption{Coefficients on the y-axis of {\sc LM full} corresponding to the
position variables on the x-axis.}
 \label{fig:posrqs}
\end{figure}
